Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Parameter variation for np scenario.

```{r fig.height=4}
cp.bic %>% 
  bind_rows(., pp.bic) %>% 
  bind_rows(., np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  facet_wrap(~model, nrow = 3) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
  theme(legend.position = "right") +
  guides(color=guide_legend(title = "Distribution \n model"))

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(median = median(min),
            mean = mean(min))

@@

```{r fig.height=6}
cp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

@@

```{r fig.height=6}
np.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate, x = individual)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

>>>>

```{r fig.height=4}
cp.bic %>% 
  bind_rows(., pp.bic) %>% 
  bind_rows(., np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  facet_wrap(~model, nrow = 3) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15, size = 0.8) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
  theme(legend.position = "right") +
  guides(color=guide_legend(title = "Distribution \n model"))

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(minimum = min(min),
            median = median(min),
            mean = mean(min))

@@

```{r fig.height=6}
cp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  dplyr::select(boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape)) +
  geom_point()
```

@@

```{r fig.height=6}

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = individual)) +
  geom_point() -> a

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = individual)) +
  geom_point() -> b

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = individual)) +
  geom_point() -> c

plot_grid(a, b, c)
```
